Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-08-29 index.qmd
add resampling code

---dd .

@@

library(flextable)
library(tidyverse)
library(tidyterra)
library(tidymodels)
library(Utilities.Package) 
library(patchwork)
library(sf) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(rnaturalearthhires)
library(ggforce) 
library(patchwork)
library(terra)
library(gt)
library(scales)
library(magick)
library(grid)
library(ggforce)
library(statebins)
library(ggridges)
library(ggspatial)
library(terrainr)
# library(ggpmisc)
library(broom)
library(stars)
library(gmodels)
library(caret)

options(scipen = 100000000)
```

@@

>>>>

@@

library(flextable)
library(tidyverse)
library(tidyterra)
# library(tidymodels)
library(Utilities.Package) 
library(patchwork)
library(sf) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(rnaturalearthhires)
library(ggforce) 
library(patchwork)
library(terra)
library(gt)
library(scales)
library(magick)
library(grid)
library(ggforce)
library(statebins)
library(ggridges)
library(ggspatial)
library(terrainr)
# library(ggpmisc)
library(broom)
library(stars)
library(gmodels)
library(caret)
library(rstudioapi)
library(terra)

options(scipen = 100000000)
# terraOptions(cores = 12)

@@

## Effect of the spatial resolution on the prediction

```{r Resampling}

img_list <- list.files("Data/BiCOME_Flights", pattern = ".tif", recursive = T, full.names = T) %>% 
  as_tibble() %>% 
  rename(path = "value") %>% 
  mutate(name = gsub(".*/","",path),
         sites = case_when(str_detect(path, "Boat1") ~ "Boat1",
                           str_detect(path, "Boat2") ~ "Boat2",
                           str_detect(path, "GafanhaHigh") ~ "GafanhaHigh",
                           str_detect(path, "GafanhaLow") ~ "GafanhaLow",
                           str_detect(path, "Horse_rooster") ~ "Horse_rooster",
                           str_detect(path, "Gois") ~ "Gois",
                           str_detect(path, "Handfisher_1") ~ "Handfisher_1",
                           str_detect(path, "Handfisher_2") ~ "Handfisher_2",
                           str_detect(path, "NorthDike") ~ "NorthDike",
                           str_detect(path, "Arz") ~ "Arz",
                           str_detect(path, "DuerHigh") ~ "DuerHigh",
                           str_detect(path, "DuerLow") ~ "DuerLow",
                           str_detect(path, "Kerdrean") ~ "Kerdrean",
                           str_detect(path, "Locmariaquer") ~ "Locmariaquer"),
         type = case_when(str_detect(name, "Preds") ~ "Pred",
                          str_detect(name, "Probs") ~ "Prob",
                          T ~ "Ortho"),
         filter = case_when(str_detect(path,"Majority_filter_21by21")~ "21",
                            str_detect(path,"Majority_filter_7by7")~ "7",
                            str_detect(path,"Majority_filter")~ "3",
                            str_detect(path,"RAW")~ "RAW",
                            T ~ "NA"),
         UTM_zone = case_when(str_detect(path, "Aveiro") ~ 32629,
                              TRUE ~ 32630)) %>% 
  dplyr::filter(!str_detect(path, ".tif.aux.xml"),
                !str_detect(path, ".tif.enp"),
                type == "Ortho")

# res_to_resample <- c(10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100,200,300,400,500,600,700,800,900,1000,1500,2000,2500,3000)
res_to_resample <- c(2000)

  # pb2 <- progress_bar$new(
  # format = "  Processing [:bar] :percent in :elapsed",
  # total = length(res_to_resample),    # Total number of iterations
  # width = 60    # Width of the progress bar
  # )

for(i in 1:nrow(img_list)){
      # pb2$tick()

  img <- terra::rast(img_list$path[i]) %>% 
    terra::project(paste0("EPSG:", img_list$UTM_zone[i]), thread = T)

  for(ii in 1:length(res_to_resample)){
    new_res <- res_to_resample[ii]/100

    r_template <- rast(ext(img), resolution = new_res, crs = crs(img))
    r_resampled <- terra::resample(img, r_template, method="bilinear", threads = T)%>% 
      terra::project("EPSG:4326", thread = T)

    if(i == 1){
      if(!dir.exists(paste0("Data/Resampling/",res_to_resample[ii],"cm"))){
       dir.create(paste0("Data/Resampling/",res_to_resample[ii],"cm"), recursive = T) 
      }
    }
    writeRaster(r_resampled, paste0("Data/Resampling/",res_to_resample[ii],"cm/",gsub(".tif",paste0("_",res_to_resample[ii],"cm.tif"),img_list$name[i])),overwrite = T)
  }

a <- list.files("Data/Resampling", recursive = T) %>% 
  as_tibble() %>% 
  rename(path = "value") %>% 
  mutate(name = gsub(".*/","",path) %>% gsub(".tif","",.)) %>% 
  pull(name) %>%
  str_c(collapse = "\", \"") %>%
  str_c("\"", ., "\"")

paste0(a)

write.csv(a, 
  "test.csv")
